Identifying regime transitions for water governance: Take the Yellow River Basin in China as case

### 2023-05-13 paper/response_letter/source/reviewer_2.tex
fix(paper): :art: 修改图片1的大小
fix(paper): :bug: 修改审稿意见返修的对应行号

\AR{} Thanks for the comment. We now improved the figure in the revised manuscript. % TODO 修改图1让它更清楚

@@

@@

\begin{quote}
    \begin{equation}
		I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}
	\end{equation}
\end{quote}

@@

\begin{quote}
    where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
\end{quote}

@@

\begin{quote}
    In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
\end{quote}

@@

\begin{quote}
    We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
\end{quote}

@@

\begin{quote}
    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river. This study only recorded the number of these ``events'' year by year according to the time they occurred.
\end{quote}

@@

\begin{quote}
    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
\end{quote}

\begin{quote}
    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
\end{quote}

\begin{quote}
    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
\end{quote}

\begin{quote}
    As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes});
\end{quote}

@@

\begin{quote}
    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
\end{quote}

@@

\begin{quote}
    To support water use in early stage (Figure~\ref{fig:summary}~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
    At the later stage (Figure~\ref{fig:summary}~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~\ref{fig:summary})~\cite{singh2019,porcher2019}.
\end{quote}

@@

\begin{quote}
    During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\
    Then, the start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use and led to institutional changes like water-saving improvements, water quota policies, and cross-boundary water transfer plans.
    Last, adaptation-oriented regime (P3: $2002 \sim 2013$) with stable high water stress resulted in trade-offs and joint regulating between water-dependent regions and sectors.
\end{quote}

>>>>

\AR{} Thanks for the comment. We now improved the figure size in the revised manuscript.

@@

\AR{} Thanks for valuable suggestion. We now added a whole paragraph to the introduction:

\begin{quote}[page=2, sline=60, eline=77]
    Research into index-based water governance assessment generally fall into two categories: those that focus on water systems, and those that concentrate on governance systems.
    On one hand, studies on governance systems typically employ an qualitative assessment to demonstrate what practices influence water governance, e.g., the OECD framework~\cite{oecd2018a}.
    For quantitative studies, due to the lack of comprehensive and detailed information on key components for water governance assessment, these studies often resort to proxy datasets of human activities to create simpler indices~\cite{varis2019,huggins2020}.
    On the other hand, studies focusing on water systems utilize intuitive indices to encapsulate the outcomes of governance, like the most widely concerned -water stress has been far developed by incorporating human's regulation step by step.
    Specifically, traditional water stress index only demands and supply~\cite{gleick1996}, water scarcity index by involving storage~\cite{damkjaer2017}, and the even more integrated SFV-index includes flexibility~\cite{qin2019}.
    Despite their usefulness, these water stress indices tend not to provide a comprehensive characterization of water governance, as they overlook the social aspect of water usage, i.e., the purpose and allocation of water use.
    As a solution, we propose an integrated water governance index (IWGI) that factors in regional water use allocations and sectoral water use purpose, thereby offering a more comprehensive quantification of governance outcomes.
\end{quote}

@@

\begin{quote}[page=6, sline=163, eline=164]
    To describe allocations $I_A$, we designed an indicator based on entropy, called Allocation Entropy Metric (AEM), which measures the degree of evenness in water allocation:
    \[I_A = AEM = \sum_{i=1}^N - \log(p_{i}) * p_{i}\]
\end{quote}

@@

\begin{quote}[page=6, sline=165, eline=166]
    where $p_{i}$ is the proportion of regional water use in $i$ to water use of the whole basin (here, $N=4$ considering divided regions in the YRB, see \textit{Supporting Information S1}).
\end{quote}

@@

\begin{quote}[page=6, sline=154, eline=156]
    In all the equations following, $R_{i, avg}$ is the average runoff in region $i$, $RC_i$ is the total storage capacities of reservoirs in the region $i$, $R_{i, std}$ is the standard deviation of runoff in the region $i$.
\end{quote}

@@

\begin{quote}[page=7, sline=168, eline=170]
    We applied the Pettitt (1979) approach to detect change-points of IWGI within continuous data, since this method has no assumptions about the distribution of the data~\cite{pettitt1979}.
\end{quote}

@@

\begin{quote}[page=Supplementary Materials]
    In addition, for capturing more specific water governance practices in the YRB had been recorded in ``Yellow River Events'' by the YRCC;\ we collected these documents from \url{http://www.yrcc.gov.cn/hhyl/hhjs/}.
    The original documents of those ``Events'' come from the Yellow River Conservancy Commission (YRCC), the agency that manages the YRB, which records and compiles ``major events'' related to the river. This study only recorded the number of these ``events'' year by year according to the time they occurred.
\end{quote}

@@

\begin{quote}[page=10, sline=247, eline=250]
    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~3~B).
\end{quote}

\begin{quote}[page=10, sline=253, eline=255]
    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~3), where increasing supply to meet demand was impractical~\cite{loch2020}.
\end{quote}

\begin{quote}[page=10, sline=260, eline=261]
    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~3~C).
\end{quote}

\begin{quote}[page=10, sline=264, eline=268]
    As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~3);
\end{quote}

@@

\begin{quote}[page=Supplementary Materials]
    Transition schema in hydrosocial cycle and water governance regimes. The natural water cycle dominates blue pathways, while socio-economic feedback dominates red.
    The large circular arrows indicate the social and hydrological processes that dominate in different stages.
    Provisioning water includes water used by human, livestock and crops while non-provisioning water includes used by industry and service.
    The processes expressed in the graph mainly include: Water supports people in provisioning ways or influence/influenced socioeconomic systems as non-provisioning ways; People manage/govern water system based on their well-beings.
    The gray thick arrow represents weaker process, while the red arrow represents more significant one.
\end{quote}

@@

\begin{quote}[page=10, sline=289, eline=296]
    To support water use in early stage (Figure~4~A), strategies tend to manage natural water processes in order to maintain the provisioning (larger) and non-provisioning water (less).
    At the later stage (Figure~4~B), emphasis is governing across the whole basin, water governance practices are adaptively designed to meet the increasing needs of the socio-economic system and carried out.
    With the above gradually shifting, the emergence of different regimes drives water governance challenges at a basin-scale: these were primarily economic and environmental before the transformation, but social and policy-related towards the end (Figure~4)~\cite{singh2019,porcher2019}.
\end{quote}

@@

\begin{quote}[page=13, sline=346, eline=353]
    During the massive supply regime (P1: $1965 \sim 1978$), water governance tended to boost water supply by constructing reservoirs and channels in the YRB.\
    Then, the start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use and led to institutional changes like water-saving improvements, water quota policies, and cross-boundary water transfer plans.
    Last, adaptation-oriented regime (P3: $2002 \sim 2013$) with stable high water stress resulted in trade-offs and joint regulating between water-dependent regions and sectors.
\end{quote}
